---
title: "Analysis of toothgrowth data"
author: "Aijing Gao"
date: "2015Äê12ÔÂ25ÈÕ"
output: word_document
---
[1]Basic explantory analysis of ToothGrowth data from datasets
```{r}
library(datasets)
library(ggplot2)
data(ToothGrowth)
help("ToothGrowth")
str(ToothGrowth)
summary(ToothGrowth)
```
This data has 60 observation, three variables
(1)len(numeric): Tooth length
(2) supp(factor): Supplement type (VC or OJ).
(3) dose(numeric): Dose in milligrams/day

[2].Summary of data by comparisons
```{r}
#make plot to campare Tooth length with different supplement type for each dosage
g<-qplot(supp,len,data=ToothGrowth, facets=~dose, main="Tooth growth of guinea pigs by different supplement type in each dose",xlab="Supplement type", ylab="Tooth length") 
g<-g+geom_boxplot(aes(fill = supp))
g

```

As we can observe in the plot, the average tooth length increases as the dose increases.

[3].Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose
Hypothesis testing
(1). Assumption: the variables are independent and identically distributed. Tooth growth follows a normal distribution.
(2). Null hypothesis for different supplement type: There is no difference in tooth growth when using the supplement OJ and VC.
Alternative hypothesis: There is a difference in tooth growth when using the supplement OJ and VC.

Null hypothesis for different dose : There is no difference in tooth growth when using different dose.
Alternative hypothesis: There is a difference in tooth growth when using different dose.

Here we are going to use two-way ANOVA for identifying effects of supplement type and dose on tooth growth

```{r}
#Perform two-way ANOVA to identify effects of supplement type, dose and their interaction
ToothGrowth$dose = factor(ToothGrowth$dose, levels=c(0.5,1.0,2.0), labels=c("low","med","high"))
ToothGrowth$supp=factor(ToothGrowth$supp,levels=c("OJ","VC"))
replications(len ~ supp+dose+supp:dose, data=ToothGrowth)
anova<- aov(len ~ supp+dose+supp:dose, data=ToothGrowth)
summary(anova)
```
As the result shows, there are two significant main effects and a significant interaction between dose and supp.
```{r}
#Perform post hoc test to do pairwise comparison in different factors
TukeyHSD(anova)
```

4. Conclusions
The above results indicate that different supplement types result in different tooth growth. Different doses of a supplement type also result in different tooth growth.